### 2021-03-24 Chapter-2/Chapter-2.tex
Updates from Overleaf

\section{Side-channel Attacks}
While there are many kinds of side-channel attacks, we only study address-based side-channel attacks in this dissertation.
Address-based side-channel attacks happen when a program accesses different memory addresses when it processes different secrets. In many situations, an attacker may shares some hardware resources (e.g., Cache, TLB, and DRAM) with the victim in today's computer system ~\cite{ge2018survey,szefer2019survey}. As a result, the attacker can probe the shared hardware resource to infer the memory accesses of the victim. While the root cause of the attack is the same, there are various approaches and an attacker can exploit the attack to retrieve the information at different granularities.

@@

\subsection{Cache-level Channel}
A CPU cache are an essential part in modern computer systems. It is a faster memory to reduce the average data accesses to the main memory.
Cache channels~\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last,184415} rely on the time difference between cache misses and cache hits. Cache channel attacks can observe cache accesses at the level of cache sets, cache lines or other granularities. 
We introduce two common attack strategies, namely Prime+Probe and
Flush+Reload. Prime+Probe targets a single cache set. An
attacker preloads the cache set with its own data and waits until the victim
executes the program. If the victim accesses the cache set and evicts part of
the data, the attacker will experience a slow measurement. 
While Flush+Reload targets a single cache line, it requires the attacker and victim share some memory. During the ``flush'' stage, the attacker flushes the ``monitored
memory'' from the cache and waits for the victim to access the memory,
who will load the sensitive information to the cache line. In the next phase,
the attacker reloads the ``monitored memory''. By measuring the time difference
brought by cache hit and miss, the attacker can further infer the sensitive information. Some other types of side-channels target different hardware
layers other than CPU cache.

>>>>

\section{Side-channel Attacks}
While there are many kinds of side-channel attacks, we focus on address-based side-channel attacks in this dissertation.
Address-based side-channel attacks happen when a program accesses different memory locations when it processes different secrets. In many situations, an attacker may shares some hardware resources (e.g., Cache, TLB, and DRAM) with the victim in today's computer system ~\cite{ge2018survey,szefer2019survey}. As a result, the attacker can probe the shared hardware resource to infer the memory accesses of the victim. While the root cause of the attack is the same, there are various approaches and an attacker can exploit the vulnerability to retrieve the information at different granularities.

@@

\subsection{Cache-level Channel}
A CPU cache are an essential part in modern computer systems. It is a smaller and faster memory which is designed to reduce the average data access costs to the main memory by storing copies of data from the main memory. When a CPU reads data from a memory location, it first checks the memory location in the cache. If it finds that the cache stores a copy of the memory location, a cache hit occurs. Otherwise, the CPU needs to read the data from the main memory and a cache miss happens.
Cache channels~\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last,184415} rely on the time difference between cache misses and cache hits. Cache channel attacks can observe cache accesses at the level of cache sets, cache lines or other granularities. We introduce two common attack strategies, namely Prime+Probe and Flush+Reload.

\textbf{Prime+Probe.} Prime+Probe targets a single cache set. 
An attacker primes the cache set with its own data and waits until the victim executes the program. After that, the attacker probes the cache by reading previously-loaded data. If the victim accesses the cache set and evicts some lines of the data, the attacker will experience a slow measurement. Under the circumstance, the attacker can know the victim must have touched some data that mapping to the same cache set.

\textbf{Flush+Reload.} Flush+Reload allow an attacker to observe the memory at a fine granularity. It targets at a cache line instead of a cache set. While Flush+Reload targets a single cache line, it requires the attacker and victim share some memory. During the ``flush'' stage, the attacker flushes the ``monitored
memory'' from the cache and waits for the victim to access the memory,
who may load the sensitive information to the cache line. On X86 machines, it can be achieved by using the \textsf{clflush} instruction. In the next phase,
the attacker reloads the ``monitored memory''. By measuring the time difference
brought by cache hit and miss, the attacker can further infer the sensitive information. Some other types of side-channels target different hardware
layers other than CPU cache.
